stupid backoff

### 2019-11-24 al_stup.Rmd
benchmarking
sqldf package transformation of major functions

TW <- corpus(train)
rm(con, train, twit, x)
summary(TW, 5)
```

@@

@@

unigs = getTables(TW, 1)
bigrs = getTables(TW, 2)
trigs = getTables(TW, 3)
rm(TW)

@@

getUnigProbs = function(unigrams) {
    #probs = unigrams %>% rename(prob = freq) %>%
    #    mutate(prob = prob/sum(prob)) %>%
    #    arrange(desc(prob), ngram)
    probs = data.table(unigrams)
    setnames(probs, "freq", "prob")
    probs = probs[, prob := prob/sum(prob)][order(prob, decreasing = T)]
    return(probs)
}

@@

>>>>

TW <- corpus(train)
rm(con, train, twit, x)
summary(TW, 5)

y = list (x1 = 1:350000,
          x2 = 350001:700000,
          x3 = 700001:1050000,
          x4 = 1050001:1400000,
          x5 = 1400000:1750000,
          x6 = 1750001:2100000,
          x7 = 2100001:2360148)
```

@@

getTablesRM = function(dat, ng) {
    dat.dfm = dfm(dat, ngrams = ng, remove_punct = T, remove_numbers = T,
                  remove = stopwords("english"))
    dat.tbl = data.table(ngram = featnames(dat.dfm), freq = colSums(dat.dfm),
                         key = "ngram")
    dat.tbl = dat.tbl[order(ngram)]
    return(dat.tbl)
}

@@

unigs = getTables(TW, 1)
bigrs = getTables(TW, 2)
trigs = getTables(TW, 3)
quads = getTables(TW, 4)
rm(TW)
gc()
```

@@

getSQLFinalProbs = function(bigPre, unigs) {
    querry = paste("SELECT * FROM trigs WHERE ngram like '", 
                   bigPre, "_%' ORDER BY freq DESC", sep = "")
    my.dat = as.data.table(sqldf(querry))
    if(nrow(my.dat) < 1) {
        my.dat = getSQLBigProbs(bigPre, bigrs)
        if(nrow(my.dat) < 1) {
            my.dat = getUnigProbs(unigs)[, freq := freq * 0.4]
            return(my.dat)
        } else {
            my.dat = my.dat[, freq := freq * 0.16]
            return(my.dat)}
    } else {
        total_count = my.dat[, sum(freq)]
        my.dat = my.dat[ , freq := freq/total_count]
        return(my.dat)
    }

getSQLTrigProbs = function(bigPre, trigrams) {
    querry = paste("SELECT * FROM trigs WHERE ngram like '", 
                   bigPre, "_%' ORDER BY freq DESC", sep = "")
    my.dat = as.data.table(sqldf(querry))
    total_count = my.dat[, sum(freq)]
    my.dat = my.dat[ , freq := freq / total_count][1:50]
    return(my.dat)
}

getSQLBigProbs = function(bigPre, bigrams) {
    w_i_1 <- str_split(bigPre, "_")[[1]][2]
    querry = paste("SELECT * FROM bigrs WHERE ngram like '",
                   w_i_1, "_%' ORDER BY freq DESC", sep = "")
    my.dat = as.data.table(sqldf(querry))
    total_count = my.dat[, sum(freq)]
    my.dat = my.dat[, freq := freq/total_count][1:50]
    return(my.dat)
}

getUnigProbs = function(unigrams) {
    #probs = unigrams %>% rename(prob = freq) %>%
    #    mutate(prob = prob/sum(prob)) %>%
    #    arrange(desc(prob), ngram)
    probs = data.table(unigrams)
    total_count = probs[, sum(freq)]
    probs = probs[order(freq, decreasing = T)][1:50][, freq := freq/total_count]
    return(probs)
}

x = sqldf("SELECT * FROM trigs WHERE ngram like 'settle_the_%' ORDER BY freq DESC")

my.dat = sqldf("SELECT * FROM trigs WHERE ngram like 'how_is_%' ORDER BY freq DESC")

mbm <- microbenchmark(
    "a" = {x <- getTrigProbs(bigPre, trigs, bigrs, unigs)},
    "b" = {y <- getSQLFinalProbs(bigPre, trigs)},
    times = 50
)

@@

test

```{r}
#performance test with unobserved regex
bigPre = "kalem_kagit"
mbm <- microbenchmark(
    "a" = {x <- getTrigProbs(bigPre, trigs, bigrs, unigs)},
    "b" = {y <- getSQLFinalProbs(bigPre, trigs)},
    times = 50
)
mbm
```

```{r}
#performance test with observed regex
bigPre = "how_is"
mbm <- microbenchmark(
    "a" = {x <- getTrigProbs(bigPre, trigs, bigrs, unigs)},
    "b" = {y <- getSQLFinalProbs(bigPre, trigs)},
    times = 50
)
mbm
```
